Blockchain as Middleware Services for\\Transactive Energy Applications

### 2017-05-03 notes/initial_writeup/paper.tex
no message

\paragraph{Controller}
The controller is responsible for stabilizing load within the microgrid and controlling it based on the load in the rest of the grid.

\todo[inline]{
\textbullet 
receives measured and expected load values from the ledger (as well as from the rest of the grid)
\textbullet 
produces a control signal that specifies the desired load for the future (may also include a tolerance level that specifies how much deviation from this load level is tolerable)
\textbullet 
may be implemented by the DSO node, as part of the RIAPS-based platform, or may be a legacy controller that interfaces with the DSO node
}

@@

\todo[inline]{
\textbullet 
control signal from DSO may change at a 4 second interval
\textbullet 
we make 4 second the basic unit of timing in our platform
(energy consumption and production are measured over 4 second units, prosumers may trade energy for durations that are multiples of 4 second units, etc.)
\textbullet 
map those timing assumptions to time interval in the transactive microgrid system
\textbullet 
discuss how supply and demand can be forecasted from energy trading between prosumers
}

@@

Time is divided into fixed-length intervals, and energy trades are specified with respect to these intervals: financial transactions promise to consume or produce a certain amount of energy in a future interval, while energy transactions record the actual amount of energy produced or consumed in an earlier interval. 
Figure~\ref{fig:timeline} shows a basic timeline of financial and energy transactions.

@@

>>>>

\paragraph{Controller}
The controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
To this end, the controller first estimates the expected load in the microgrid based on outstanding energy trades on the ledger.
By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the load in the microgrid needs to be decreased or increased.
Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
The controller may be implemented by the DSO node, as part of the RIAPS-based platform, or may be a legacy controller that interfaces with the DSO node.

@@

Timing is a crucial part of our platform.
For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete time intervals.
The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
In our implementation, for example, the default length of the time interval is 4 seconds, which corresponds to how frequently the control signal of the DSO changes.

@@

All transactions for energy trading are specified with respect to these discrete intervals: financial transactions promise to consume or produce a certain amount of energy in a future interval, while energy transactions record the actual amount of energy produced or consumed in an earlier interval. 
Figure~\ref{fig:timeline} shows a basic timeline of financial and energy transactions.

@@

\subsection{Control Algorithm}

\todo[inline]{
\textbullet 
receives measured and expected load values from the ledger (as well as from the rest of the grid)
\textbullet 
produces a control signal that specifies the desired load for the future (may also include a tolerance level that specifies how much deviation from this load level is tolerable)
}
